Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is a merged and final version of two conference papers, \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}, with a unified and streamlined presentation.}

### 2020-07-18 journal paper/itcs18paper/app-examples.tex
In "TS is monotone", added independence assumption.
In AppB: added prior into the setup.

Throughout, we consider a standard MAB setting. There are $T$ rounds and $K$ arms. In each round $t\in [T]$, the algorithm chooses an arm $a_t\in A$ and receives a reward $r_t\in[0,1]$ for this arm, drawn from a fixed but unknown distribution. The set of all arms is $A$; mean reward of arm $a$ is denoted $\mu_a$.

We let
    $\rew(t) = \mu_{a_t}$
denote the instantaneous mean reward of the algorithm.

Instantaneous regret is denoted
    $\IReg(t) := \max_{a\in A} \mu_a - \mu_{a_t}$,
so that
    $\BIR(t) = \E[\IReg(t)]$.

@@

\begin{theorem}[\citet{Selke-BE-2020}]\label{thm:TS-mono}
\Thompson is \bmonotone.
\end{theorem}

\begin{corollary}
\Thompson satisfies $\BIR(t)\leq \tildeO(t^{-1/2})$.
\end{corollary}

>>>>

We consider a simple setting of Bayesian MAB with Bernoulli rewards. There are $T$ rounds and $K$ arms. In each round $t\in [T]$, the algorithm chooses an arm $a_t\in A$ and receives a reward $r_t\in\{0,1\}$ for this arm, drawn from a fixed but unknown distribution. The set of all arms is $A$; mean reward of arm $a$ is denoted $\mu_a$. \asedit{The mean reward vector $\mu = (\mu_a:\; a\in A)$ is drawn from a common Bayesian prior $\priorMu$.}
We let
    $\rew(t) = \mu_{a_t}$
denote the instantaneous mean reward of the algorithm.

%Instantaneous regret is denoted
%    $\IReg(t) := \max_{a\in A} \mu_a - \mu_{a_t}$,
%so that
%    $\BIR(t) = \E[\IReg(t)]$.

@@

\begin{theorem}[\citet{Selke-BE-2020}]\label{thm:TS-mono}
\asedit{Assume the prior $\priorMu$ is independent across arms.} Then \Thompson is \bmonotone. Consequently, it satisfies $\BIR(t)\leq \tildeO(t^{-1/2})$.
\end{theorem}
